---
title: "Assignment03"
author: "Erik Fichter"
date: "9/19/2020"
output: html_document
---
```{r}
library(tidyverse)
library(ggplot2)
```



## Analysis for correlation between residential buildings (value, type, size etc) and commute time to work



```{r Loading Data, results='hide', message=FALSE}

ma_re_trans_data<- read.csv("2018 RE Transportation.csv")
ma_re_trans_data

```




# Correlation between two continuous variables - Pearson’s correlation

## Property Value (Con) and Traveltime (Con)

While the correlation between property value and traveltime is weak, it is statistically significant. 

```{r}
correlation <- cor.test(ma_re_trans_data$VALP, ma_re_trans_data$JWMNP)

correlation
```

As seen in the figure, this positive correlation means that as value increases, traveltime grows.

```{r}
ggplot(ma_re_trans_data, aes(x = VALP, y = JWMNP)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Value of Property (USD)") +
  scale_y_continuous(name = "Traveltime (minutes)", 
                     breaks = seq(0, 6000, by = 10),
                     labels = paste("", 
                      prettyNum(seq(0, 6000, by = 10),
                      big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 200, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1], digits = 2), 
                         "to",
                         prettyNum(correlation$conf.int[2], digits = 2)),
           hjust = 0)
```


## Nuber of Bedrooms (Con) and Traveltime (Con)

While the correlation between bedrooms and traveltime is weak, it is statistically significant. 

```{r}
correlation2 <- cor.test(ma_re_trans_data$BDSP, ma_re_trans_data$JWMNP)

correlation2
```

As seen in the figure, this very small but positive correlation means that as the number of bedrooms increase, traveltime grows. A reason for that might be that bigger homes are further away from the CBD and office hubs as they are more affordable in the outskirts. 

```{r}
ggplot(ma_re_trans_data, aes(x = BDSP, y = JWMNP)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Number of Bedrooms") +
  scale_y_continuous(name = "GTraveltime (minutes)", 
                     breaks = seq(0, 6000, by = 10),
                     labels = paste("", 
                      prettyNum(seq(0, 6000, by = 10),
                      big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 200, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1], digits = 2), 
                         "to",
                         prettyNum(correlation$conf.int[2], digits = 2)),
           hjust = 0)
```

# Gross Monthly Rent (Con) and Traveltime (Con)

There is no critical correlation between Gross Monthly Rent and Traveltime to work. WHY ???

```{r}
correlation <- cor.test(ma_re_trans_data$GRNTP, ma_re_trans_data$JWMNP)

correlation
```

```{r}
ggplot(ma_re_trans_data, aes(x = GRNTP, y = JWMNP)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Monthly Rent") +
  scale_y_continuous(name = "Traveltime (minutes)", 
                     breaks = seq(0, 6000, by = 10),
                     labels = paste("", 
                      prettyNum(seq(0, 6000, by = 10),
                      big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 200, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1], digits = 2), 
                         "to",
                         prettyNum(correlation$conf.int[2], digits = 2)),
           hjust = 0)
```


# Relationship between a continuous variable and categorical variable with more than two levels - Analysis of Variance (ANOVA)

## Type of Structure (Cat) and Traveltime (Con)

The ANOVA indicates that with a p value less than .1, there is a significant relationship between the type of structure and the traveltime to work.

```{r}
anova <- aov(JWMNP ~ BLD_label, data = ma_re_trans_data)

summary(anova)
```
Since this relationship is statistically significant, I'll run a Tukey's HSD test to see the magnitude of differences among the difference category, followed by a boxplot to visualize the differences.

```{r}
differences <- TukeyHSD(anova)

as_tibble(cbind(pair = row.names(differences$BLD_label),
                differences$BLD_label))
```
The boxplot allows for an easy understanding of how the means and overall distribution of traveltime differs from each the type of building.

```{r}
ggplot(ma_re_trans_data, aes(x = BLD_label, y = JWMNP)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Type of structure") +
  scale_y_continuous(name = "Traveltime to Work", 
                     breaks = seq(0, 1000, by = 10),
                     labels = paste("", 
                                    prettyNum(seq(0, 1000, by = 10),
                                              big.mark = ","))) 
```


## Means of Transportation (Cat) and Traveltime (Con)

The ANOVA indicates that with a p value less than .1, there is a significant relationship between the type of structure and the traveltime to work.

```{r}
anova <- aov(JWMNP ~ JWTR_label, data = ma_re_trans_data)

summary(anova)
```
```{r}
differences <- TukeyHSD(anova)

as_tibble(cbind(pair = row.names(differences$JWTR_label),
                differences$JWTR_label))
```
```{r}
ggplot(ma_re_trans_data, aes(x = JWTR_label, y = JWMNP)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45)) +
  scale_x_discrete(name = "Means of Transportation") +
  scale_y_continuous(name = "Traveltime to Work", 
                     breaks = seq(0, 1000, by = 20),
                     labels = paste("", 
                                    prettyNum(seq(0, 1000, by = 20),
                                              big.mark = ","))) 
```


# Relationship between two categorical variables - Chi-square test

## Type of Structure (Cat) and Transportation Type (Cat)


```{r}
chi_sq <- chisq.test(ma_re_trans_data$BLD_label, ma_re_trans_data$JWTR_label != "Car, truck, or van") 

chi_sq
```
little to no correlation


```{r}
observation <- chi_sq
observation
```

```{r}
expectation <- chi_sq
expectation
```

