---
title: "Assignment01"
author: "Erik Fichter"
date: "9/8/2020"
output: html_document
---

```{r load libraries}
library(tidycensus)
library(tidyverse)
library(knitr)
```
# Variables used:
I decided to explore the housing value in relation to the place of work. In order to understand the relation I focused on the following variables. Geographically I focused on Massachusetts as it is the area in the United States I am most familiar with. The source of the data is from https://www.census.gov/:

  1. Value of the property (continuous): VALP
  
  2. Amount and type of units within the structure (categorical): BLD
  
  3. Number of bedrooms (continuous): BDSP
  
  4. Travel time to work (continuous): JWMNP
  
  5. Means of transportation (categorical): JWTR

```{r load person-level microdata variables}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```

```{r}
hh_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "housing", year == 2018, survey == "acs1")
```

```{r}
area_vars_2018 <- load_variables(2018, "acs1")
```

```{r}
hh_data <- get_pums(variables = c("VALP", 
                                  "BLD",
                                  "BDSP",
                                  "JWMNP",
                                  "JWTR"),
                    
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%

filter(VALP > 0) %>%
filter(JWMNP > 0) %>%


select(VALP, BLD_label, BDSP, JWMNP, JWTR_label)

                    

knitr::kable(hh_data[1:10,])                
  

```


```{r}
hh_data
```
